The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-08-26 src/paper/application.tex
Archive repo and point to new one.

\newcommand*{\thisdraft}{\normalsize{This draft: \today}} 
\newcommand*{\firstdraft}{\normalsize{First draft: 27 March 2023}} 
\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/ValueOfIntermediation/application.pdf}{stanmart.github.io/ValueOfIntermediation/application.pdf}}}

>>>>

\newcommand*{\thisdraft}{\normalsize{This draft: \today}} 
\newcommand*{\firstdraft}{\normalsize{First draft: 27 March 2023}} 
\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/phd-thesis/application.pdf}{stanmart.github.io/phd-thesis/application.pdf}}}

### 2024-08-26 src/paper/theory.tex
Archive repo and point to new one.

\newcommand*{\thisdraft}{\normalsize{This draft: \today}} 
\newcommand*{\firstdraft}{\normalsize{First draft: 2 August 2022}} 
\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/ValueOfIntermediation/theory.pdf}{stanmart.github.io/ValueOfIntermediation/theory.pdf}}}

>>>>

\newcommand*{\thisdraft}{\normalsize{This draft: \today}} 
\newcommand*{\firstdraft}{\normalsize{First draft: 2 August 2022}} 
\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/phd-thesis/theory.pdf}{stanmart.github.io/phd-thesis/theory.pdf}}}
